Dialect: A Compact Line Notation Based on SMILES

### 2022-06-10 manuscript.tex
Drops atom rank. closes #110

Transformation of tree to graph can be aided by a \textit{fastener} (Figure~\ref{fig:fastener}). A fastener is a key/value store whose keys are bridge indexes and whose values are an aggregation of atom rank with the bond attributes \ttt{order}, \ttt{elided}, and \ttt{direction}. Odd insertions (first, third, etc.) associate the bridge index with the aggregation and return \ttt{None}. Even insertions (second, fourth, etc.) remove the associated aggregation and return it. A fastener is paired with a depth-first traversal of the tree to be transformed. On encountering a gap an insertion is made. If the return value is an aggregation, it is used together with the current gap bond attributes and atom rank to create a bond and place it within the molecular graph.

>>>>

Transformation of tree to graph can be aided by a \textit{fastener} (Figure~\ref{fig:fastener}). A fastener is a key/value store whose keys are bridge indexes and whose values are a tuple composed of: (1) the identifier of the last atom added to the graph; and (2) the bridge bond attributes \ttt{order}, \ttt{elided}, and \ttt{direction}. Odd insertions (first, third, etc.) associate the bridge index with the tuple and return \ttt{None}. Even insertions (second, fourth, etc.) remove the previously-associated tuple and return it. A fastener is paired with a depth-first traversal of the tree to be transformed. On encountering a bridge, an insertion is made. If the return value is a tuple, it is used together with the current gap bond attributes and atom identifier to create a bond and place it within the molecular graph.
